A Convolutional Neural Network for Outsole Recognition\tnoteref{t1}

### 2020-03-30 paper/paper-revision.Rnw
Incorporate scanner context

Although footwear impressions are more commonly used in practice for footwear analysis than outsole images, early prototypes of a footwear scanner have suggested that cameras are more robust than pressure scanners for placement in public locations that may experience inclement weather or other non-controlled conditions. Thus, \fix{we move forward by considering how to assess similarity of tread patterns in images, in particular.} More specifically, this assessment is done by identifying a set of relevant features and using image analysis methods to detect the presence or absence of the features in each image, and then defining similarity measures based on those features to determine how many shoes have a tread pattern similar to the pattern of interest.

\fix{We are working to dev a scanner using photo technology. It takes pics like Zappos. While images are degraded in some ways, the fundamental reqs are sim. We want to dev the methodology for this before we get actual data.}

\fix{manual collection citations: presentation by Sandy Parent, benedict et al, benedict cites another, the one that says college students and criminals are basically the same}

>>>>

Although footwear impressions are more commonly used in practice for footwear analysis than outsole images, early prototypes of a footwear scanner have suggested that cameras are more robust than pressure scanners for placement in public locations that may experience inclement weather or other non-controlled conditions. \mt{Thus, we are working to develop a scanner using photo technology} \fix{(reference/cite image of the scanner)}. \mt{This scanner would take pictures of shoe outsoles, much like images that are currently found on the websites of online shoe retailers \fix{(reference/cite test image of  an outsole on the scanner)}. Although the images from the scanner are more degraded in some ways than those found from online retailers, the fundamental requirements to analyze such data would be similar.} Therefore, \fix{we move forward by considering how to assess similarity of tread patterns in images of outsoles, in particular.} More specifically, this assessment is done by identifying a set of relevant features and using image analysis methods to detect the presence or absence of the features in each image, and then defining similarity measures based on those features to determine how many shoes have a tread pattern similar to the pattern of interest.
